---
title: "Financial condition of bank"
output: html_document
---
# 10.1

**Financial condition of bank using logistc regression**

##Data load and drop obs, 

```{r}
Banks <- read.csv("Banks.csv")
#View(Banks)

Banks <- Banks[, -c(1,3)]

Banks$Financial.Condition <- factor(Banks$Financial.Condition, levels = c(1,0))
```

##Make logistic regression model
##Run logistic regression on datasset, predictor variables = X

```{r}
logit.class <- glm(Financial.Condition~TotExp.Assets+TotLns.Lses.Assets, family = binomial(link='logit'), data=Banks)

options(scipen=999)

#summary(logit.class)
plot(logit.class)
names(logit.class)
coef(logit.class)
exp(coef(logit.class))
```

#1.Write the estimated equation that associates the financial condition of a bank with its two predictors in three formats:

i) Logit Format: Logit(Financial Condition = Weak) = -14.721 + 89.834 x (TotExp/Assets) + 8.731 x (TotLns&Lses/Assets)

ii) Odds Format: Odds(Financial Condition = Weak) = e^(-14.721 + 89.834 x TotExp/Assets + 8.731 x TotLns&Lses/Assets)

iii) Probabiloity Format: Probability(Financial Condition = Weak) = 1 / (1 + e^(-14.721 + 89.834 x TotExp/Assets + 8.731 x TotLns&Lses/Assets))

#2. Consider a new bank whose total loans and leases/assets ratio = 0.6 and total expenses/assets ratio = 0.11.

```{r}
newbank <- data.frame("TotExp.Assets"=0.11, "TotLns.Lses.Assets"=0.6)

# The logit = 0.3993
logit <- -14.721 + 89.834 * 0.11 + 8.731 * 0.6
logit

# The odds = 1.4908
odds <- exp(logit)
odds

#The probability = 0.4015
probability <- 1 / (1 + odds)
probability

# The classification of the bank : Not weak.
new.pred <- predict(logit.class, newbank)
new.pred
```

#3. Compute the threshold that should be used if we want to make a classification based on the odds of being financially weak, and the threshold for the corresponding logit.

# If the cutoff value is 0.5 based on odds, then the threhold of odds is equal to 1, and the corresponding logit is equal to 0.

```{r}
cutoff = 0.5
odds = cutoff/(1-cutoff)
odds

logit = log(odds)
logit
```

#4.Interpret the estimated coefficient for the total loans & leases to total assets ratio interms of the odds of being financially weak.

# The coefficent for TotLns&Lses/Assets has a positive number, which means if TotLns&Lses/Assets increase, the odds of belonging to class 1 (weak) will also increase.
# And a single unit increase in TotLns&Lses/Asset, holding other predictors constant, is associated with an increase in the odds that the financial condition is weak by a factor of exp(8.731).

#5.To minimize the expected cost of misclassification, should the
cutoff value for classification (which is currently at 0.5) be increased or decreased?

# In this case, we should decrease the cutoff value to avoid the misclassification that a bank in poor financial condition is misclassified as financially strong.

```{r}
p <- ifelse(logit.class$fitted.values >= 0.5,0,1)
table(p, Banks$Financial.Condition)
p <- ifelse(logit.class$fitted.values >= 0.9,0,1)
table(p, Banks$Financial.Condition)
p <- ifelse(logit.class$fitted.values >= 0.1,0,1)
table(p, Banks$Financial.Condition)
p <- ifelse(logit.class$fitted.values >= 0,0,1)
table(p, Banks$Financial.Condition)
p <- ifelse(logit.class$fitted.values >= 0.03,0,1)
table(p, Banks$Financial.Condition)
```